Contention Management for 5G

### 2017-02-10 article/article.tex
preuve 3nt

       \begin{center}
      \includegraphics[scale=0.2]{BBU1.jpeg}

@@

	\end{algorithmic}
	\end{algorithm}
      \paragraph{Period}
	This algorithm gives us a solution without waiting times in a maximum period $3.\tau.c$, if we have $c$ routes.\\
	Suppose that we have a period of $3.\tau.c$ slots, divided in $\tau$ macro-slots. Let us call {\em forward period} the period in the central node when the messages goes to RRH to BBU, and {\em backward period} the period when the messages comes back in the other way. Put a message in the first slot of size $\tau$ in the forward period, such that the corresponding area in the backward period is free.This message takes at most 2 slots of time $\tau$ in the backward period.\\
	\todo{Dessin qui illustre ça}\\
	When $k < c$ messages are put in the forward period, and we want to add another message, there is $3.c - k$ free slots of size $\tau$ in the forward period. Those $3.c - k$ gives us $3.c - k$ possible slots in the backward periods.\\
	The $k$ messages uses at most $2k$ slots of size $\tau$ used in the backward period. Since $k<c$,  $2k < 3.c - k$, thus using the pigeonhole principle, there is at least one free slot in the backward period for the new message.

>>>>

       \begin{center}

@@

	\end{algorithmic}
	\end{algorithm}
      \paragraph{Period}
	This algorithm gives us a solution without waiting times in a maximum period $3.\tau.c$, if we have $c$ routes.\\
	Suppose that we have a period of $3.\tau.c$ slots, divided in $\tau$ macro-slots. Let us call {\em forward period} the period in the central node when the messages goes to RRH to BBU, and {\em backward period} the period when the messages comes back in the other way. Put a message in the first slot of size $\tau$ in the forward period, such that the corresponding area in the backward period is free.This message takes at most 2 slots of time $\tau$ in the backward period.\\
      \begin{center}
      \includegraphics[scale=0.2]{ex3nt.png}
      \end{center}
	When $k < c$ messages are put in the forward period, and we want to add another message, there is $3.c - k$ free slots of size $\tau$ in the forward period. Those $3.c - k$ gives us $3.c - k$ possible slots in the backward periods.\\
	The $k$ messages uses at most $2k$ slots of size $\tau$ used in the backward period. Since $k<c$,  $2k < 3.c - k$, thus using the pigeonhole principle, there is at least one free slot in the backward period for the new message.
